### 2018-04-26 doc/paper.tex
Implementing the generic K-fold compensated Horner's.
Also adding the full flop counts to the write-up.

Empirically, it seems the process takes
\[(15K^2 - 34K + 26)T_n + K + 5\]
flops to evaluate a degree \(n\) polynomial. (Here \(T_n\) is the
\(n\)th triangular number.)

>>>>

After implementing for \(K = 2, 3, \ldots, 12\) and instrumenting all
relevant floating point operations, the \(K\)-fold Horner requires
\[(5 \cdot 2^K - 8)n + \left((K + 8) 2^K - 12K - 6\right)\]
flops to evaluate a degree \(n\) polynomial. As a comparison, the
non-compensated form of Horner requires \(2n\) flops. Of these,
\(\left(2^{K - 1} - 1\right)n - 2^{K - 1}(K - 3) - 2\) are
FMA (fused-multiply-add) instructions.

After implementing for \(K = 2, 3, 4, 5\) and instrumenting all relevant
floating point operations, the \(K\)-fold de Casteljau requires
\[(15K^2 - 34K + 26)T_n + K + 5\]
flops to evaluate a degree \(n\) polynomial. (Here \(T_n\) is the
\(n\)th triangular number.) As a comparison, the non-compensated form of
de Casteljau requires \(3 T_n + 1\) flops. Of these, \((3K - 4)T_n\) are
FMA instructions. On hardware that doesn't support FMA,
every FMA will be exchanged for 10 \(\ominus\)'s and 6 \(\otimes\)'s so the
count will increase by \((10 + 6 - 1)(3K - 4)T_n\).
